### 2019-09-04 manuscript/manuscript.tex

\gc{It is unclear how strong the fluctuations would have to be to
  generate a genome-wide average signal of fluctuating selection from
  temporal covariances. For example,there many loci could still show a
  signal of fluctuating selection, but their average signals could be
  overwhelmed by other signals of fluctuating selection. To
  investigate whether there was an genome-wide excess} of loci showing evidence
  of fluctuating selection we re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \gc{\textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy},\gc{the bionomial null model does not
  include random evolutionary variation in allele frequencies. }

@@

%Without
%such \gc{an evolutionary null} distribution, we do not have a statistical expectation for the number of
%variants across the genome with frequency trajectories that spuriously fit the
%pattern of seasonal fluctuating selection. We found that we can

>>>>

\gc{It is unclear how strong the fluctuations would have to be to
  generate a genome-wide average signal of fluctuating selection from
  temporal covariances. For example,there many loci could still show a
  signal of fluctuating selection, but their average signals could be
  overwhelmed by other signals of fluctuating selection. To
  investigate whether there was an genome-wide excess} of loci showing evidence
  of fluctuating selection we re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \gc{\textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy},\gc{the bionomial null model does not
  include random evolutionary variation in allele frequencies. }
% =======
% We were concerned that this might be due to a flaw in our methods. To address
% this concern, we first ensured that our temporal-covariance matrix bias
% correction was working as expected. We find that it corrects the relationship
% between depth and both variance and covariance (Supplementary Figure
% \ref{suppfig:bergland-correction}) as expected. We then re-analyzed the data of
% \parencite{Bergland2014-ij} using the same seasonal fluctuating model as the
% original paper. This model is a Binomial logit-linked GLM fit per-locus, where
% the Spring/Fall seasons are encoded as a dummy variable, and are regressed on
% the frequency data. We use the same binomial weighting procedure as
% \textcite{Bergland2014-ij}, where the weights are determined by the effective
% number of chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and
% $d_t$ are the number of diploid individuals and the read depth at timepoint
% $t$, respectively). We fit this model on all loci marked as used in the VCF
% provided with the \textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p).
% Overall, our p-values for the Wald test for each locus closely match those of
% the original paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times
% 10^{-16}$; see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison}
% A), and the histograms of the p-values are nearly identical (Supplementary
% Figure \ref{suppfig:bergland-pvalue-comparison} B). 
% >>>>>>> d95c3549a10dc0037f40a54cb8b41f9d412ed1ed

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/bergland-correction-plot.pdf}

  \caption{The variance and covariances from the \texticite{Bergland2014-ij}
    study, calculated in 100kb genomic windows plotted against average depth in
    a window before and after bias correction. Each panel has a least-squares
    estimate between the variance and covariance, and the average depth.
    The bias correction procedure is correcting sampling bias in both the variance
    and covariance such that the relationship with depth is constant. Colors
    indicate the different chromosomes of \emph{D. melanogaster}; we have
    excluded the X chromosome (yellow points; chromosome 4 was not in the
    original study) from the regression due to large differences in average
    coverage.}

  \label{suppfig:bergland-correction}
\end{figure}
